Hydrodynamics of a Semipermeable Vesicle Under Flow and Confinement

### 2020-12-29 vesicle_code/docs/permeableVes/main.tex
working on contracting fig
fixed fig 6 and 7

\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/contractingComposite.tikz}
  \else
  \includegraphics{figures/contractingComposite.pdf}
  \fi
  \caption{\label{fig:contractingComposite} A contracting geometry
  similar to the experimental device in~\cite{wu2015critical}. The
  channel width varies from $18\mu$m to $1.8\mu$m, and it repeats every
  $45\mu$m. The fluid flux along the red regions is into the vesicle,
  and the fluid flux along the blue regions is out of the vesicle.
  (a--c): The ability for a semipermeable vesicle to pass through the
  constriction depends on the semipermeability rate. (d--f): The ability
  for a semipermeable vesicle to pass through the constriction depends
  on the flow rate. (g): A semipermeable vesicle passing through six
  periods of the constricting geometry. (h): The reduced area with the
  marks representing shapes in (g). (i): The vesicle velocity with the
  marks representing shapes in (g).}
\end{figure*}

\begin{figure}[htp]
  \ifTikz
  \input{figures/contractingComposite2.tikz}
  \else
  \includegraphics{figures/contractingComposite2.pdf}
  \fi
  \caption{\label{fig:contractingComposite2} Vesicle reduced area and
  velocity vs.~time.}
\end{figure}

@@

\todo[inline]{Break up figure 6 in half}

>>>>

\begin{figure}[htp]
  \centering
  \ifTikz
  \input{figures/contractingComposite.tikz}
  \else
  \includegraphics{figures/contractingComposite.pdf}
  \fi
  \caption{\label{fig:contractingComposite} A contracting geometry
  similar to the experimental device in~\cite{wu2015critical}. The
  channel width varies from $18\mu$m to $1.8\mu$m, and it repeats every
  $45\mu$m. The fluid flux along the red regions is into the vesicle,
  and the fluid flux along the blue regions is out of the vesicle.
  (a--c): The ability for a semipermeable vesicle to pass through the
  constriction depends on the semipermeability rate. (d--f): The ability
  for a semipermeable vesicle to pass through the constriction depends
  on the flow rate.}
\end{figure}

\begin{figure}[htp]
  \ifTikz
  \input{figures/contractingComposite2.tikz}
  \else
  \includegraphics{figures/contractingComposite2.pdf}
  \fi
  \caption{\label{fig:contractingComposite2} Vesicle reduced area and
  velocity vs.~time. Permeability rate is $\beta = 10^{-3}$ and maximum
  velocity is $18\mu$m/s. (a): A semipermeable vesicle passing through
  six periods of the contracting geometry. (b): The reduced area with
  the marks representing shapes in (a). (c): The vesicle velocity with
  the marks representing shapes in (a). In (b) and (c), the bottom
  x-axis is the $x$-coordinate of the center of mass, and the upper
  x-axis is time.}
\end{figure}

@@
